---
title: "Toolbox: Experimental evidence"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
    code_folding: hide
    theme: flatly
    highlight: monochrome
---
This part of the online supplement is a digital toolbox in the form of a dynamic table that offers an overview of published evidence . For publication details, links to articles, and detailed results, ___click on the arrow or the “Expand” button___ to the left of the intervention type. To search through the whole table, use the search function below. Use the smaller search fields under a column’s header to search within that column. You can sort a column by clicking on its header, or sort multiple columns by holding the shift key while sorting. 


```{r setup, include=FALSE, echo=FALSE}

if(!require("pacman"))
  install.packages("pacman")
library(pacman)
p_load(
  "tidyverse",
  "here",
  "readr",
  "workflowr",
  "readxl",
  "dplyr",
  "ggplot2",
  "reactable",
  "glue",
  "htmltools",
  "jsonlite",
  "sparkline"
)


knitr::opts_chunk$set(echo = FALSE
)
```



```{r load and filter data, include = FALSE, echo = FALSE}



dat_path2 <-
  here("data/toolbox_evidence.xlsx")
data2 <- read_xlsx(dat_path2)

versions <- jsonlite::read_json("output/infos_refined.json", simplifyDataFrame = TRUE)


```


```{r, include = FALSE, echo = FALSE}

#based on https://glin.github.io/reactable/articles/cran-packages/cran-packages.html
# function for details row

row_details <- function(index) {
  data <- data2[index, ] 
   # pkg <- data2[data2$Intervention == df2$Intervention[index],
  urls <- unlist(strsplit(gsub(",", " , ", data$OSF_link, perl = TRUE), "[ \n]"))
 doi <- unlist(strsplit(gsub(",", " , ", data$DOI, perl = TRUE), "[ \n]"))

  pkg_field <- function(name, ...) {
    if (any(is.na(...))) NULL
    else tagList(div(class = "detail-label", name), ...)
  }
 

  detail <-  htmltools::div(
    class = "package-detail",
    div(class = "detail-header", data$Intervention
        # , span(class = "detail-title", data$References_long)
        ),
    div(
      class = "detail-description", data$References_long),
       # pkg_field("Reference", data$References_long),
      pkg_field("DOI", lapply(doi, function(url) {
      if (grepl("https?://", url)) tags$a(href = url, url)
      else if (identical(url, ",")) ", "
      else url
    })),
    pkg_field("Open data", lapply(urls, function(url) {
      if (grepl("https?://", url)) tags$a(href = url, url)
      else if (identical(url, ",")) ", "
      else url
    })),
    pkg_field("Abstract", data$Abstract),
      pkg_field("Method", data$Method),
    # pkg_field("Design", data$Design),
     pkg_field("Test stimuli", data$"Test stimuli"),
     pkg_field("Additional measures", data$Measures),
     pkg_field("Comment", data$Comment)
      )

  # if (versions[[data$References]]!= "") {
    archived <- pkg_field(
      "Results",
      reactable(
        versions[[data$References]],
        pagination = FALSE,
        defaultColDef = colDef(headerClass = "header"),
        columns = list(
          Study = colDef(minWidth = 100),
          N = colDef(minWidth = 80),
           Description= colDef(minWidth = 400),
          "Effect size" = colDef(minWidth = 200),
           Comments = colDef(name = "Results", minWidth = 400)
          ),
        fullWidth = FALSE,
        class = "archived-table",
        theme = reactableTheme(cellPadding = "8px 12px")
      ))
    
    detail <- tagAppendChild(detail, archived)
 
  detail
  
}



```

```{r, include = TRUE, echo = FALSE}



# add expand all button https://github.com/glin/reactable/issues/28#issuecomment-962796616
#https://glin.github.io/reactable/articles/javascript-api.html

htmltools::browsable(tagList(
  tags$button("Click here to expand/collapse all rows",
              onclick = "Reactable.toggleAllRowsExpanded('evidence-table')"),
  
  
  reactable(
    data2[, c(
      "Intervention",
      "References",
      "Experimental setting",
      "Design",
      "Treatment",
      "Outcome variable",
      "Sample size",
      "Sample Country",
      "Sample demographics",
      "Recruitment",
      "Longevity",
      "Main findings"
    )],
    elementId = "evidence-table",
    searchable = TRUE,
    showSortable = TRUE,
    filterable = TRUE,
    striped = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    width = 1800,
    defaultColDef = colDef(minWidth = 75),
    showPageSizeOptions = TRUE,
    pageSizeOptions = c(4, 8, 12),
    defaultPageSize = 6,
    theme = reactableTheme(
      borderColor = "#dfe2e5",
      stripedColor = "#f6f8fa",
      highlightColor = "#f0f5f9",
      
      style = list(fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif"),
      searchInputStyle = list(width = "100%")
    ),
    
    columns = list(
      Intervention = colDef(
        minWidth = 80,
        rowHeader = TRUE,
        style = list(fontWeight = 600)
      ),
      References = colDef(minWidth = 100),
      "Experimental setting" = colDef(minWidth = 90,  aggregate = "frequency"),
      
      Design = colDef(minWidth = 80,  aggregate = "frequency"),
      "Sample Country" = colDef(aggregate = "frequency"),
      "Outcome variable" = colDef(minWidth = 100),
      Treatment = colDef(minWidth = 120),
      "Sample demographics" = colDef(
        name = "Demographics",
        minWidth = 100,
        aggregate = "frequency"
      ),
      "Main findings" = colDef(minWidth = 160),
      Recruitement = colDef(aggregate = "frequency"),
      "Sample size" = colDef(align = "left", format = colFormat(digits = 0))
      
    ),
    details = colDef(
      width = 75,
      name = "Details",
      details = row_details,
      cell = function()
        htmltools::tags$button("Expand", class = "button2")
    )
    
  )
))

```
[Privacy policy](https://ai_society.mpib.dev/intervention_toolbox/privacy.html) - [Imprint/Provider Identification](https://ai_society.mpib.dev/intervention_toolbox/terms.html)

```{css, echo=FALSE}
p {
 font-size: 20px;
 width: 1200px;
  margin: 10px 15px 15px 0px;
 }

li {
  font-size: 20px;
  }


h1 {
  font-size: 32px;
  width: 1200px;
}



 button { color: white;
 background-color: rgba(14, 114, 186, 0.7);
 margin: 10px 15px 15px 0px;
 border: none;
 padding: 7px 7px;
 <!-- text-align: center; -->
 <!-- text-decoration: none; -->
 <!-- <!-- display: inline-block; --> -->
 <!-- font-size: 16px -->
  }
  
  
 .button2 { color: black;
 background-color: rgba(14, 114, 186, 0.1);
 margin: 10px 30px 0px 5px;
 border: none;
 padding: 4px 4px;
 font-size: 12px;
  }


body {
  # background-color: rgba(176, 219, 234, 0.5);
   <!-- margin-top: 10px; -->
  <!-- margin-left: 5px; -->
 padding-left: 0px;
   width: 50%;
}

.btn-workflowr {
  display: none
}


.btn-workflowr-sessioninfo {
  visibility: hidden
}

.btn-default {
  visibility: hidden
}

.package-detail {
  padding: 24px;
  box-shadow: inset 0 1px 3px #dbdbdb;
  background: hsl(213, 20%, 99%);
}

.detail-label {
  margin: 20px 0 4px;  
  font-size: 14px;
  color: rgba(0, 0, 0, 0.6);
}

.detail-header {
  margin-bottom: 16px;
  font-size: 20px;
  font-weight: 600;
}

.detail-title {
  margin-left: 18px;
  font-size: 15px;
  font-weight: 600;
  color: rgba(0, 0, 0, 0.8);
}

.detail-description {
  font-size: 14px;
}

.archived-table {
  border: 1px solid hsl(213, 33%, 93%);
  border-radius: 4px;
  box-shadow: 0 2px 7px 0 rgba(0, 0, 0, 0.05);
  font-size: 14px;
}

```
