---
title: "Toolbox: Conceptual overview"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    # rmdcss::html_air
    # toc: false
    # code_folding: hide
    theme: flatly
    highlight: monochrome
    # css: modest.css

---

This part of the online supplement is a digital toolbox in the form of a dynamic table that offers a conceptual overview of interventions. For useful links and other details ___click on the arrow or the “Expand” button___ to the left of the intervention type. To search through the whole table, use the search function below. Use the smaller search field under a column’s header to search within that column. You can sort a column by clicking on its header, or sort multiple columns by holding the shift key while sorting. 


```{r setup, include=FALSE}

# devtools::install_github("nwstephens/rmdcss")

# install.packages("workflowr")

if(!require("pacman")) install.packages("pacman"); library(pacman)
p_load("tidyverse", "here", "readr",  "workflowr",
          "readxl", "jtools", "broom", "kableExtra", "knitr",
          "sjlabelled", "dplyr", "janitor", "ggplot2", "kableExtra", "wesanderson",  "webshot", "ggthemes", "questionr", "shiny", "formattable", "DT", "reactable", "png", "glue", "htmltools", "reactablefmtr", "rmdcss")



options(scipen = 999)

knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```


```{r, html function, include = FALSE}
html <- function(x, inline = FALSE) {
  container <- if (inline) htmltools::span else htmltools::div
  container(dangerouslySetInnerHTML = list("__html" = x))
}
```

```{r load and filter data, include=FALSE}


dat_path <-
  here("data/toolbox_concept.xlsx")
data <- read_xlsx(dat_path, na = "") 

# ?read_xlsx

df1 <- data  %>% 
  select(- Outtakes, - Experts) 
# %>% 
#    mutate(Details = glue('Links: {Links}', .sep = "")) %>% 
#   select( - Links) 
# %>% 
#   filter (Intervention != "Rebuttals of science denialism")
  # mutate (Logo = "", .before = "Description")
colnames(df1)



```



```{r}
#http://haozhu233.github.io/kableExtra/use_kableExtra_with_formattable.html
```

```{r, include = FALSE, echo = FALSE}

#based on https://glin.github.io/reactable/articles/cran-packages/cran-packages.html
# function for details row

row_details <- function(index) {
  data <- df1[index, ]
   # pkg <- data2[data2$Intervention == df2$Intervention[index],
  urls <- unlist(strsplit(gsub(",", " , ", data$Links, perl = TRUE), "[ \n]"))
  evidence <- unlist(strsplit(gsub(",", " , ", data$Evidence_link, perl = TRUE), "[ \n]"))

  pkg_field <- function(name, ...) {
    if (any(is.na(...))) NULL
    else tagList(div(class = "detail-label", name), ...)
  }
 

  detail <-  htmltools::div(
    class = "package-detail",
    pkg_field("References", data$Reference_concept),
    # div(class = "detail-header", data$Intervention
    #     # , span(class = "detail-title", data$References_long)
    #     ),
    # div(
    #   class = "detail-description", data$Intervention),
        pkg_field("Useful links", lapply(urls, function(url) {
      if (grepl("https?://", url)) tags$a(href = url, url)
      else if (identical(url, ",")) ", "
      else url
        })),
     pkg_field("For a selection of experimental evidence click here", lapply(evidence, function(url) {
      if (grepl("https?://", url)) tags$a(href = url, url)
      else if (identical(url, ",")) ", "
      else url
        }))
        #    pkg_field("Abstract", data$Abstract),
    # pkg_field("Comment", data$Comment),
    # pkg_field("Method", data$Method),
    # # pkg_field("Design", data$Design),
    #  pkg_field("Stimuli", data$Stimuli),
    #  pkg_field("Additional measures", data$Measures)
      )
}

```

```{r, include = TRUE, echo =FALSE}

htmltools::browsable(
  tagList(
    tags$button(
      "Click here to expand/collapse all rows",
      onclick = "Reactable.toggleAllRowsExpanded('concept-table')"
    ),

reactable(
 df1[, c("Intervention", "Description", "Example", "Conceptual framework", "Category", "Problem", "Targeted outcomes", "Audience",  "Implementation", "Scalability","Limitations")],
  elementId = "concept-table",
  searchable = TRUE,
 filterable = TRUE,
  showSortable = TRUE,
  striped = TRUE,
  highlight = TRUE,
  bordered = TRUE,
  width = 1800,
  defaultColDef = colDef(minWidth = 100),
  showPageSizeOptions = TRUE,
  pageSizeOptions = c(4, 8, 12),
  defaultPageSize = 11,
  theme = reactableTheme(
    borderColor = "#dfe2e5",
    stripedColor = "#f6f8fa",
    highlightColor = "#f0f5f9",
    # cellPadding = "8px 12px",
    style = list(fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif"),
    searchInputStyle = list(width = "100%")
  ),
  columns = list(
    Intervention = colDef(
      minWidth = 110,
       align = "center",
      html = TRUE,
      style = list(fontWeight = 600),
      cell = function(value) {
        img_src <- knitr::image_uri(sprintf("./logos/%s.png", value))
        image <- img(src = img_src,
                     width = "100px",
                     alt = value)
        tagList(div(style = list(display = "inline-block", width = "120px"), image),
                value)
      }
    ),
    Description= colDef(minWidth = 150),
    Example = colDef(minWidth = 150),
    "Conceptual framework" = colDef(minWidth = 120),
    "Targeted process" = colDef(minWidth = 160),
    Implementation = colDef(minWidth = 160),
    Scalability = colDef(minWidth = 140),
    Limitations = colDef(minWidth = 170),
    Links = colDef(show = FALSE)),
    details = colDef(width = 75, name = "Details", details = row_details,
     cell = function() htmltools::tags$button("Expand", class = "button2")
                  )
      )
  ))

```

[Privacy policy](https://ai_society.mpib.dev/intervention_toolbox/privacy.html) - [Imprint/Provider Identification](https://ai_society.mpib.dev/intervention_toolbox/terms.html)


```{css, echo=FALSE}
p {
 font-size: 20px;
 width: 1200px;
  margin: 10px 15px 15px 0px;
 }



li {
  font-size: 20px;
  }



h1 {
  font-size: 32px;
  width: 1200px;
}



 button { color: white;
 background-color: rgba(14, 114, 186, 0.8);
 margin: 10px 15px 15px 0px;
 border: none;
 padding: 7px 7px;
 <!-- text-align: center; -->
 <!-- text-decoration: none; -->
 <!-- <!-- display: inline-block; --> -->
 <!-- font-size: 16px -->
  }

 .button2 { color: black;
 background-color: rgba(14, 114, 186, 0.1);
 margin: 10px 30px 0px 5px;
 border: none;
 padding: 4px 4px;
 font-size: 12px;
  }


body {
  # background-color: rgba(176, 219, 234, 0.5);
   <!-- margin-top: 10px; -->
  <!-- margin-left: 5px; -->
 padding-left: 0px;
   width: 50%;
}

.btn-workflowr {
  display: none
}


.btn-workflowr-sessioninfo {
  visibility: hidden
}

.btn-default {
  visibility: hidden
}

.package-detail {
  padding: 24px;
  box-shadow: inset 0 1px 3px #dbdbdb;
  background: hsl(213, 20%, 99%);
}

.detail-label {
  margin: 20px 0 4px;  
  font-size: 14px;
  color: rgba(0, 0, 0, 0.6);
}

.detail-header {
  margin-bottom: 16px;
  font-size: 20px;
  font-weight: 600;
}

.detail-title {
  margin-left: 18px;
  font-size: 14px;
  font-weight: 400;
  color: rgba(0, 0, 0, 0.6);
}

.detail-description {
  font-size: 14px;
}

.archived-table {
  border: 1px solid hsl(213, 33%, 93%);
  border-radius: 4px;
  box-shadow: 0 2px 7px 0 rgba(0, 0, 0, 0.05);
  font-size: 14px;
}

```

