---
title: "Toolbox: Experimental evidence"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
    code_folding: hide
    theme: flatly
    highlight: monochrome
---
This part of the online supplement is a digital toolbox in the form of a dynamic table that offers an overview of published evidence . For publication details, links to articles, and detailed results, ___click on the arrow or the “Expand” button___ to the left of the intervention type. To search through the whole table, use the search function below. Use the smaller search fields under a column’s header to search within that column. You can sort a column by clicking on its header, or sort multiple columns by holding the shift key while sorting. 


```{r setup, include=FALSE, echo=FALSE}

if(!require("pacman")) install.packages("pacman"); library(pacman)
p_load("tidyverse", "here", "readr",  "workflowr",
          "readxl",  "dplyr", "ggplot2", "reactable", "glue", "htmltools", "jsonlite", "sparkline")

# install.packages("reactable")

# options(scipen = 999)


knitr::opts_chunk$set(echo = FALSE)
```



```{r load and filter data, include = FALSE, echo = FALSE}



dat_path2 <-
  here("data/toolbox_evidence.xlsx")
data2 <- read_xlsx(dat_path2)
# %>% 
#   filter(Intervention == "Inoculation")
# %>%
# filter(Intervention == "Accuracy prompts" |Intervention == "Debunking"|Intervention == "Friction"|Intervention == "Lateral reading in education"|Intervention == "Lateral reading online"|Intervention == "Media literacy tips"|Intervention == "Rebuttals of science denialism"|Intervention == "Self-reflection tools"|Intervention == "Social norms"|Intervention == "Warning & fact-checking labels")
       # |
# |Intervention == "Lateral reading in education"|Intervention == "Lateral reading online"|Intervention == "Media literacy tips"|Intervention == "Rebuttals of science denialism"|Intervention == "Self-reflection tools"|Intervention == "Social norms"|Intervention == "Warning & fact-checking labels")


# |Intervention == "Debunking"|Intervention == "Friction"|Intervention == "Inoculation"|Intervention == "Lateral reading in education"|Intervention == "Lateral reading online"|Intervention == "Media literacy tips"|Intervention == "Rebutals of science denialism"
# 
# versions <- jsonlite::read_json("data/results_all.json", simplifyDataFrame = TRUE)
# versions <- jsonlite::read_json("output/infos_raw.json", simplifyDataFrame = TRUE)
versions <- jsonlite::read_json("output/infos_refined.json", simplifyDataFrame = TRUE)


glimpse(versions[[1]])

colnames(data2)



```


```{r, include = FALSE, echo = FALSE}

#based on https://glin.github.io/reactable/articles/cran-packages/cran-packages.html
# function for details row

row_details <- function(index) {
  data <- data2[index, ] 
   # pkg <- data2[data2$Intervention == df2$Intervention[index],
  urls <- unlist(strsplit(gsub(",", " , ", data$OSF_link, perl = TRUE), "[ \n]"))
 doi <- unlist(strsplit(gsub(",", " , ", data$DOI, perl = TRUE), "[ \n]"))

  pkg_field <- function(name, ...) {
    if (any(is.na(...))) NULL
    else tagList(div(class = "detail-label", name), ...)
  }
 

  detail <-  htmltools::div(
    class = "package-detail",
    div(class = "detail-header", data$Intervention
        # , span(class = "detail-title", data$References_long)
        ),
    div(
      class = "detail-description", data$References_long),
       # pkg_field("Reference", data$References_long),
      pkg_field("DOI", lapply(doi, function(url) {
      if (grepl("https?://", url)) tags$a(href = url, url)
      else if (identical(url, ",")) ", "
      else url
    })),
    pkg_field("Open data", lapply(urls, function(url) {
      if (grepl("https?://", url)) tags$a(href = url, url)
      else if (identical(url, ",")) ", "
      else url
    })),
    pkg_field("Abstract", data$Abstract),
      pkg_field("Method", data$Method),
    # pkg_field("Design", data$Design),
     pkg_field("Test stimuli", data$"Test stimuli"),
     pkg_field("Additional measures", data$Measures),
     pkg_field("Comment", data$Comment)
      )

  # if (versions[[data$References]]!= "") {
    archived <- pkg_field(
      "Results",
      reactable(
        versions[[data$References]],
        pagination = FALSE,
        defaultColDef = colDef(headerClass = "header"),
        columns = list(
          Study = colDef(minWidth = 100),
          N = colDef(minWidth = 80),
           Description= colDef(minWidth = 400),
          "Effect size" = colDef(minWidth = 200),
           Comments = colDef(name = "Results", minWidth = 400)
          ),
        fullWidth = FALSE,
        class = "archived-table",
        theme = reactableTheme(cellPadding = "8px 12px")
      ))
    
    detail <- tagAppendChild(detail, archived)
 
  detail
  
}



```

```{r, include = TRUE, echo = FALSE}


# add expand all button https://github.com/glin/reactable/issues/28#issuecomment-962796616
#https://glin.github.io/reactable/articles/javascript-api.html

htmltools::browsable(
  tagList(
    tags$button(
      "Click here to expand/collapse all rows",
      onclick = "Reactable.toggleAllRowsExpanded('evidence-table')"
    ),
    
    
reactable(data2[, c("Intervention", "References", "Experimental setting", "Design", "Treatment", "Outcome variable", "Sample size",  "Sample Country", "Sample demographics", "Recruitment", "Longevity", "Main findings")],
          elementId = "evidence-table",
          searchable = TRUE, showSortable = TRUE, filterable = TRUE,
                  striped = TRUE,   highlight = TRUE,   bordered = TRUE, width = 1800, 
          defaultColDef = colDef(minWidth = 75),
            showPageSizeOptions = TRUE, pageSizeOptions = c(4, 8, 12), defaultPageSize = 6,
                  theme = reactableTheme(
                      borderColor = "#dfe2e5",
                      stripedColor = "#f6f8fa",
                      highlightColor = "#f0f5f9",
                      # cellPadding = "8px 12px",
                      style = list(fontFamily = "-apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif"),
                      searchInputStyle = list(width = "100%")),
          # groupBy = "Intervention",
                  columns = list(
                    Intervention = colDef(minWidth = 80, rowHeader = TRUE, style = list(fontWeight = 600)),
                      References = colDef(minWidth = 100),
                      "Experimental setting" = colDef(minWidth = 90,  aggregate = "frequency"),
                    # "Paradigm" = colDef(minWidth = 100,  aggregate = "frequency"),
                      Design = colDef(minWidth = 80,  aggregate = "frequency"),
                      "Sample Country" = colDef(aggregate = "frequency"),
                      "Outcome variable" = colDef(minWidth = 100),
                       Treatment = colDef(minWidth = 120),
                      "Sample demographics" = colDef(name = "Demographics", minWidth = 100,  aggregate = "frequency"),
                      "Main findings" = colDef(minWidth = 160),
                      Recruitement = colDef(aggregate = "frequency"),
                      "Sample size" = colDef(align = "left", format = colFormat(digits = 0))
  #                     "Longevity measured?" = colDef(minWidth = 100, aggregate = "frequency"
  #                                        , cell = function(value) {
  #   # Render as an X mark or check mark
  #   if (value == "No") "\u274c" else "\u2714\ufe0f"
  # }
  # )
                  ),
                  details = colDef(width = 75, name = "Details", 
                  details = row_details, 
                  cell = function() htmltools::tags$button("Expand", class = "button2")
                              )
  #         ,
  # wrap = FALSE,
  # class = "packages-table",
  # rowStyle = list(cursor = "pointer")
  # # theme = reactableTheme(cellPadding = "8px 12px")
  )
)
)

# ?htmltools::tags$button

```
[Privacy policy](https://ai_society.mpib.dev/intervention_toolbox/privacy.html) - [Imprint/Provider Identification](https://ai_society.mpib.dev/intervention_toolbox/terms.html)
<!-- ### Note on effect sizes: -->

<!-- *Cohen's d* -->
<!-- Interpretation suggested by Cohen: -->

<!--     .2: Small effect size -->
<!--     .5: Medium effect size -->
<!--     .8: or higher: Large effect size -->

<!-- *Partial eta squared (η2p)* "describes a proportion of variability in a sample associated with an independent variable; it is calculated as the ratio between the sum of squares for a particular factor in an ANOVA and that sum of squares combined with the sum of squares for its specific error term." -->
<!-- The following rules of thumb are commonly used to interpret values for Partial eta squared: -->

<!--     .01: Small effect size -->
<!--     .06: Medium effect size -->
<!--     .14 or higher: Large effect size -->

<!-- Note that these are general suggestions for interpretations, and that "the values should be considered in the context of research in an area." -->
<!-- https://www.bps.org.uk/psychologist/methods-why-are-effect-sizes-still-neglected -->

```{css, echo=FALSE}
p {
 font-size: 20px;
 width: 1200px;
  margin: 10px 15px 15px 0px;
 }

li {
  font-size: 20px;
  }


h1 {
  font-size: 32px;
  width: 1200px;
}



 button { color: white;
 background-color: rgba(14, 114, 186, 0.7);
 margin: 10px 15px 15px 0px;
 border: none;
 padding: 7px 7px;
 <!-- text-align: center; -->
 <!-- text-decoration: none; -->
 <!-- <!-- display: inline-block; --> -->
 <!-- font-size: 16px -->
  }
  
  
 .button2 { color: black;
 background-color: rgba(14, 114, 186, 0.1);
 margin: 10px 30px 0px 5px;
 border: none;
 padding: 4px 4px;
 font-size: 12px;
  }


body {
  # background-color: rgba(176, 219, 234, 0.5);
   <!-- margin-top: 10px; -->
  <!-- margin-left: 5px; -->
 padding-left: 0px;
   width: 50%;
}

.btn-workflowr {
  display: none
}


.btn-workflowr-sessioninfo {
  visibility: hidden
}

.btn-default {
  visibility: hidden
}

.package-detail {
  padding: 24px;
  box-shadow: inset 0 1px 3px #dbdbdb;
  background: hsl(213, 20%, 99%);
}

.detail-label {
  margin: 20px 0 4px;  
  font-size: 14px;
  color: rgba(0, 0, 0, 0.6);
}

.detail-header {
  margin-bottom: 16px;
  font-size: 20px;
  font-weight: 600;
}

.detail-title {
  margin-left: 18px;
  font-size: 15px;
  font-weight: 600;
  color: rgba(0, 0, 0, 0.8);
}

.detail-description {
  font-size: 14px;
}

.archived-table {
  border: 1px solid hsl(213, 33%, 93%);
  border-radius: 4px;
  box-shadow: 0 2px 7px 0 rgba(0, 0, 0, 0.05);
  font-size: 14px;
}

```
