---
title: "Toolbox: World map of evidence"
output: 
  html_document:
    toc: true
    toc_float: true

---

This section of the online supplement offers an interactive world map showcasing the studies featured in our evidence toolbox. By double-clicking the intervention name in the legend, you can isolate that specific intervention on the map. When you hover over the circles on the map, it will display the counts of studies by country.

```{r setup, include=FALSE}
# Load required packages
if(!require("pacman")) install.packages("pacman")
library(pacman)
### to do: re-check which packages were actually used
p_load(
  "tidyverse", "here", "readr",  "workflowr",
  "readxl", "jtools", "broom", "kableExtra",
  "knitr", "maps", "countrycode", "plotly", "htmlwidgets"
)

options(scipen = 999)

knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, fig.width = 8.37)
```

```{r read_and_filter_data, echo=FALSE}
# read in data
df <- read_excel("data/toolbox_evidence.xlsx", na = c("", "NA"))


# drop irrelevant columns & data
country_data <- df %>%
  select(Intervention, `Sample Country`) %>%
  rename(Country = `Sample Country`) %>%
  # deal with multiple countries & interventions
  # account for paper w/ 2 studies (only the second is relevant)
  separate_rows(Country, sep = "2: ") %>%
  # drop entries without specific origins
  filter(!grepl("international|global", Country, ignore.case = TRUE)) %>%
  # expand lists in `Country` into separate entries
  separate_rows(Country, sep = ", ") %>%
  separate_rows(Country, sep = " and the ") %>%
  # don't double count entries with "and" in them
  # but still consider entries with multiple interventions
  # !!! NOTE: this will no longer behave properly if entries are added which:
  #     - have multiple types of interventions named in one row separated by the string " and "
  #     - AND at least one of the categories containing the string " and "
  #       (e.g., "Debunking and rebuttals") is included in this list
  #     - solution (and also probably better to keep formatting uniform):
  #       - separate multiple `Intervention`s with " & " or ", "
  mutate(
         Intervention = case_when(
           (grepl(" and ", Intervention) &
              # don't modify entries with "and" in their category titles
              !grepl("Debunking and|Lateral reading and|Warning and", Intervention)) ~
             str_replace(Intervention, " and ", " & "),
           TRUE ~ Intervention
         )) %>%
  # separate & remove the "Multiple interventions:" tag
  separate_rows(Intervention, sep = ": ") %>%
  filter(!grepl("multiple", Intervention, ignore.case = TRUE)) %>%
  # expand lists of `Intervention`s into separate entries
  separate_rows(Intervention, sep = " & ") %>%
  separate_rows(Intervention, sep = ", ") %>%
  # fix entries to fit official country names & intervention categories
  mutate(
         Country = case_when(
           # fix some inconsistencies/trailing spaces
           grepl("United St", Country) ~ "United States",
           grepl("South Africa", Country) ~ "South Africa",
           grepl("Taiwan", Country) ~ "Taiwan",
           TRUE ~ Country
         ),
         Intervention = case_when(
           # format to categories
           grepl("Debunking|Rebuttals", Intervention, ignore.case = TRUE) ~ "Debunking & rebuttals",
           grepl("Lateral|verification", Intervention, ignore.case = TRUE) ~ "Lateral reading & verification strategies", 
           grepl("credibility", Intervention, ignore.case = TRUE) ~ "Source-credibility labels",
           grepl("Warning|checking", Intervention, ignore.case = TRUE) ~ "Warning & fact-checking labels",
           TRUE ~ Intervention
         )) %>%
  drop_na()


# count interventions by country
counts <- country_data %>%
  group_by(Country, Intervention) %>%
  summarise(n = n())

# join counts with country longitude/latitude (from Google – https://developers.google.com/public-data/docs/canonical/countries_csv)
countries <- read.csv("data/countries.csv")
counts <- left_join(counts, countries, by = c("Country" = "name"))

# clean data
counts <- counts %>%
  select(-c(X)) %>%
  rename(country_code = country) %>%
  group_by(Country) %>%
  mutate(num_interventions = n_distinct(Intervention)) %>%
  # sort
  arrange(desc(n)) %>%
  # order of interventions/country
  mutate(rank_order = row_number())

```
```{r adjust_longitudes}

# if a country has multiple interventions, add or subtract from latitude to plot
offset_lon <- function(df) {
  df <- df[order(-df$n),]
  df <- df %>%
    group_by(Country) %>%
    subset(!is.na(Country))
  by_country <- split(df, df$Country)
  # for each country
  for (i in seq_along(by_country)) {
    # extract current country data
    curr_df <- by_country[[i]]
    # skip entries w/ no longitude given
    if (is.na(curr_df$longitude[1])) {
      next
    }
    # find middle row number
    mid_row <- nrow(curr_df) %/% 2 + 1
    # number of unique interventions
    unique_ints <- nrow(curr_df)
    # sum of # of interventions
    int_count <- sum(curr_df$n)
    if (unique_ints > 1) {
      if (unique_ints == 2) {
        # if there are only 2 points to plot
        # make equidistant from original point
        curr_df$longitude[1] <- curr_df$longitude[1] - 2*log(curr_df$n[1] + curr_df$n[2])
        curr_df$longitude[2] <- curr_df$longitude[2] + 2*log(curr_df$n[1] + curr_df$n[2])
      } else {
        # iterate backward from middle
        for (j in rev(1:(mid_row-1))) {
          curr_df$longitude[j] <- curr_df$longitude[j+1] - 2*log(curr_df$n[j] + curr_df$n[j+1])
        }
        if (unique_ints > 2) {
          # iterate forward from middle
          for (j in (mid_row+1):nrow(curr_df)) {
            curr_df$longitude[j] <- curr_df$longitude[j-1] + 2*log(curr_df$n[j] + curr_df$n[j-1])
          }
        }
      }
      # for unbalanced groups of points, shift all points to the right
      if (sum(curr_df$n[mid_row:unique_ints]) <= 3) {
        curr_df$longitude <- curr_df$longitude + 2*log(sum(curr_df$n[mid_row:unique_ints]))
      }
    }
    # replace current country data
    by_country[[i]] <- curr_df
  }
  # recombine data
  df_edited <- do.call(rbind, by_country)
  return(df_edited)
}


# calculate longitude offsets
counts_adjusted <- offset_lon(counts)
```

```{r plotly_plot, fig.height=8, fig.width=10}

# define color palette


wes_colors <- c("#e3342f", "#f6993f", "#ffed4a", "#228B22", "#91c591", "#34495E", "#3498DB", "#9561e2", "#f66d9b")


# create plot
plotly_map <- plot_geo(counts_adjusted) %>%
  add_markers(
    x = ~longitude,
    y = ~latitude,
    size = ~n,
    sizes = c(10, 600),
    color = ~Intervention,
    text = ~paste(Country, "<br>Intervention:", Intervention, "<br>Count:", n),
    hoverinfo = "text",
    colors = wes_colors,
    opacity = 0.85
  ) %>%
  layout(
    title = list(
      text = "",
      xref = "paper"
    ),
    # set width, height, & legend specs so they are coerced into 3 columns
    width = 1000,
    height = 600,
    legend = list(
      orientation = "h",
      yanchor = "bottom",
      xanchor = "middle",
      x = 0.04
      # xref = "paper",
      # y = 0.1,
    ),
    # to make it display properly in the knitted doc
    # adjust/remove if rendering html separately
    margin = list(
      l = 0,
      r = 100
    ),
    showlegend = TRUE,
    geo = list(
      showland = TRUE,
      landcolor = toRGB("grey90"),
      countrycolor = toRGB("white"),
      countrywidth = 0.35,
      coastlinecolor = toRGB("grey80"),
      coastlinewidth = 0.5,
      showcountries = TRUE,
      fitbounds = "locations"
       )
  )

# print
plotly_map
```


```{r ggplot_plot, include = FALSE}

world <- map_data("world")

ggplot_map <- ggplot() +
  geom_map(
    data = world, map = world,
    aes(map_id = region),
    color = "white", fill = "grey85", size = 0.1
  ) +
  coord_sf(ylim = c(-50, 70), xlim = c(-120, 150), datum = NA) +
  geom_point(
    data = counts_adjusted,
    aes(longitude, latitude, fill = Intervention, size = n),
    shape = 21, alpha = 0.65, stroke = 0
  ) +
  scale_size_continuous(
    range = c(2, 12),
    # guide = "none",
    # if we wanted to include a key for the scale of the points & their corresponding values
    breaks = c(min(counts_adjusted$n), max(counts_adjusted$n)),
    labels = c(str(min(counts_adjusted$n)), str(max(counts_adjusted$n)))
  ) +
  scale_fill_manual(values = wes_colors) +
   guides(
    # coerce legend into 3 column shape;
    # increase the size of the legend's key markers
    fill = guide_legend(ncol = 3, override.aes = list(size = 7))
  ) +
  ggtitle("Interventions by Country") +
  theme_void() +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text = element_text(size = 11),
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5)
  )

# print
ggplot_map
```

```{r, include = FALSE}
unique_sizes <- unique(counts_adjusted$n)

ggplot_map2 <- ggplot() +
  geom_map(
    data = world, map = world,
    aes(map_id = region),
    color = "white", fill = "grey85", size = 0.1
  ) +
  coord_sf(ylim = c(-50, 70), xlim = c(-120, 150), datum = NA) +
  geom_point(
    data = counts_adjusted,
    aes(longitude, latitude, fill = Intervention, size = n),
    shape = 21, alpha = 0.65, stroke = 0
  ) +
scale_size_continuous(
    range = c(2, 12),
    breaks = unique_sizes,
    labels = unique_sizes,
    guide = guide_legend(title = "Size")
  ) +
  scale_fill_manual(values = wes_colors) +
  guides(
    fill = guide_legend(ncol = 3, override.aes = list(size = 7))
  ) +
  ggtitle("Interventions by Country") +
  theme_void() +
  theme(
    legend.position = "bottom",
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 11),
    plot.title = element_text(size = 18, face = "bold", hjust = 0.5)
  )



# print
print(ggplot_map2)

```


```{r ggplot_plot save, include = FALSE}
ggsave(
  filename = here("output/figure_map.pdf"),
  plot = ggplot_map2,
  dpi = 300,
  units = 'cm',
  height = 10,
  width = 24
)

```
----






[Privacy policy](https://ai_society.mpib.dev/intervention_toolbox/privacy.html) - [Imprint/Provider Identification](https://ai_society.mpib.dev/intervention_toolbox/terms.html)

```{css, echo=FALSE}
p {
 font-size: 20px;
 width: 1200px;
  margin: 10px 15px 15px 0px;
 }



li {
  font-size: 20px;
  }



h1 {
  font-size: 32px;
  width: 1200px;
}

body {
  # background-color: rgba(176, 219, 234, 0.5);
  # margin-left: 0px;
  # padding-left: 0px;
   width: 100%;
}
# h1 {
#   color: white;
#   text-align: center;
# }
# p {
#   color: red;
#   text-align: center;
# }

.btn-workflowr {
  display: none
}


.btn-workflowr-sessioninfo {
  visibility: hidden
}

.btn-default {
  visibility: hidden
}


```
